---
title: "Data Science Homework 5"
author: "Boya Guo"
date: "11/9/2018"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(echo = TRUE,
                      fig.width = 6,
                      fig.asp = .6,
                      out.width = "90%")
theme_set(theme_bw() + 
  theme(legend.position = "bottom"))
```

## Problem 1
```{r p1.1:read in data}
read_csv_data = function(x) {
  
  read_csv(x) %>% 
    mutate(name = x)
}

file_list = list.files("./data/") %>% paste0("./data/", .)

```

```{r p1.2: tidying data}
hw5 = map_dfr(file_list, read_csv_data) %>%
  mutate(arm = ifelse(str_detect(name, "con") == TRUE, "control", "experimental"),
         subject_id = substr(name, 12, 13)) %>% 
  gather(key = week, value = observation, week_1:week_8) %>% 
  mutate(week = str_replace(week, "week_", ""),
         id = as.factor(subject_id),
         week = as.numeric(week)) %>% 
  select(id, arm, week, observation) %>% 
  janitor::clean_names()

hw5
```

```{r p1.3: spaghetti plot}
  ggplot(hw5,aes(x = week, y = observation, color = id)) + 
  geom_line() +
  facet_grid(.~ arm) +
    labs(
    title = "The change of observations across time in the control and experimental arms" ,
    x = "Weeks" ,
    y = "Observations"
    ) +
  theme(legend.position = "left")
```

According to the plot produced, we could find that there is an increase in the observations of experimental groups as time increases. However, the change in the control group seems to fluctuate between -1.25 and 3.75, with no apparent change as time increases.


## Problem 2
```{r p2.1 read in data}
homicide_raw = read_csv("./data/homicide_data.csv") %>%
  janitor::clean_names()
```


```{r p2.1 homicides and unsolved homicides}
homicide = homicide_raw %>% 
  mutate(city_state = str_c(city, state, sep = ', ')) 
```
The raw data contains `r nrow(homicide_raw)` observations and `r ncol(homicide_raw)` variables. 
There are 52179 obeservations in the dataset.
Variables in the dataset are: uid, reported date, victim's name, race, age, sex, city, state, latitude, longtitude and disposition.
The data includes 50 cities in the United States.


```{r p2.2 homicides and unsolved homicides within cities}
p2.1 = homicide %>% 
  group_by(city_state) %>% 
  mutate(total_homicides = n()) %>% 
  filter(disposition == 'Closed without arrest' | disposition == 'Open/No arrest') %>% 
  mutate(unsolved_homicides = n()) %>% 
  distinct(city_state, total_homicides, unsolved_homicides) %>%
  select(city_state, total_homicides, unsolved_homicides) 


p2.1
```


```{r p2.3 Baltimore}
Baltimore = p2.1 %>% 
  filter(city_state == "Baltimore, MD") 
  
Baltimore_prop = prop.test(Baltimore$unsolved_homicides, Baltimore$total_homicides, correct = TRUE)

save(Baltimore_prop,file = "Baltimore_prop.RData")

Baltimore_prop %>% 
  broom::tidy() %>% 
    janitor::clean_names() %>% 
    select(estimate, conf_low, conf_high) %>% 
    knitr::kable(digits = 3) 
```

The estimated proportion of homicides is 0.6456 lies between a 95% confidence interval of (0.628,0.663).


```{r p2.4 all cities}

```


